The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-08-27 src/paper/literature_review.tex
Go back to longer version, nature submission, update references. (#6)

These shortcomings have motivated variations of agent-based simulation models where
moving particles have been replaced by contact networks for households, work and random
contacts. The OpenABM-Covid-19 model by \citet{Hinch2021} and the model by
\citet{Aleta2020} are the closest in spirit to ours.

The OpenABM-Covid-19 model by \citet{Hinch2021} also uses detailed contact networks for
workplaces, schools and households and can evaluate the effect of several NPIs. The main
focus of their application are contact tracing policies. Recently they have also added
support for multiple virus strains and vaccinations.

>>>>

These shortcomings have motivated variations of agent-based simulation models
where moving particles have been replaced by contact networks for households,
work and random contacts. The OpenABM-Covid-19 model by \citet{Hinch2021a} and
the model by \citet{Aleta2020} are the closest in spirit to ours.

The OpenABM-Covid-19 model by \citet{Hinch2021a} also uses detailed contact
networks for workplaces, schools and households and can evaluate the effect of
several NPIs. The main focus of their application are contact tracing policies
\citep{Abueg2021}. Recently they have also added support for multiple virus
strains and vaccinations.
